Parallel-in-time methods for Particle Simulations

### 2024-11-30 paper/main.tex
Added results

The integration part is the part which usually is dependent on some previous time step and thus can't be easily parallelized. In order to solve this problem, multiple techniques were devised with the most widely known one being the parareal algorithm.

@@

\begin{table*}[htbp]
\caption{Comparison of running times taken by different configurations of the simulator}
\begin{center}
\begin{tabular}{ccrrrrrrrrcc}
\toprule
Program & Time &  n CPUs & Segments & $N_\text{Coarse}$ & $N_{\text{Fine}}$ & $N_{\text{Final}}$ $^{\mathrm{a}}$ & Iters $^{\mathrm{b}}$ & Abs. error $^{\mathrm{c}}$ & Rel. error $^{\mathrm{d}}$ & CPU time & Runtime \\
\midrule
parareal & $10^4\text{days}$ & 32 & 32 &  5000 &  50000 & 1600000 & 1 & 0.0030 AU & 1.00\% & 00:05:33 & 00:00:35 \\
parareal & $10^4\text{days}$ & 16 & 16 & 10000 & 100000 & 1600000 & 2 & 0.0031 AU & 1.03\% & 00:08:12 & 00:01:07 \\
serial & $10^4\text{days}$ & 1 & 1 & N/A & 1600000 & 1600000 & N/A & 0 AU & 0\% & 00:02:34 & 00:02:34 \\
\bottomrule
\multicolumn{11}{l}{$^{\mathrm{a}}$ Resulting number of steps (equal to number of segments times $N_\text{Fine}$)} \\
\multicolumn{11}{l}{$^{\mathrm{b}}$ Number of iterations required for convergence ($\varepsilon = 10^{-3}$)} \\
\multicolumn{11}{l}{$^{\mathrm{c}}$ Maximum difference from the corresponding serial computation across the trajectory} \\
\multicolumn{11}{l}{$^{\mathrm{d}}$ Maximum relative error across the trajectory compared to the serial computation}
\end{tabular}
\label{runtimes}
\end{center}
\end{table*}

>>>>

The integration part is the part which usually is dependent on some previous time step and thus can't be easily parallelized. In order to make it parallelizable, multiple techniques were devised, one of them being the parareal algorithm.

@@

\begin{table*}[htbp]
\caption{Comparison of running times taken by different configurations of the simulator}
\begin{center}
\begin{tabular}{ccrrrrrrrrcc}
\toprule
Program & Time &  n CPUs & Segments & $N_\text{Coarse}$ & $N_{\text{Fine}}$ & $N_{\text{Final}}$ $^{\mathrm{a}}$ & Iters $^{\mathrm{b}}$ & Abs. error $^{\mathrm{c}}$ & Rel. error $^{\mathrm{d}}$ & CPU time & Runtime \\
\midrule
parareal & $10^4\text{days}$ & 32 & 32 &  5000 &  50000 & 1600000 & 1 & 0.0030 AU & 0.97\% & 00:05:33 & 00:00:35 \\
parareal & $10^4\text{days}$ & 16 & 16 & 10000 & 100000 & 1600000 & 2 & 0.0031 AU & 1.03\% & 00:08:12 & 00:01:07 \\
serial & $10^4\text{days}$ & 1 & 1 & N/A & 1600000 & 1600000 & N/A & 0 AU & 0\% & 00:02:34 & 00:02:34 \\
\bottomrule
\multicolumn{11}{l}{$^{\mathrm{a}}$ Resulting number of steps (equal to number of segments times $N_\text{Fine}$)} \\
\multicolumn{11}{l}{$^{\mathrm{b}}$ Number of iterations required for convergence ($\varepsilon = 10^{-3}$)} \\
\multicolumn{11}{l}{$^{\mathrm{c}}$ Maximum difference from the corresponding serial computation across the trajectory} \\
\multicolumn{11}{l}{$^{\mathrm{d}}$ Maximum relative error across the trajectory compared to the serial computation}
\end{tabular}
\label{runtimes}
\end{center}
\end{table*}
